Towards a standardized evaluation of multiple imputation routines

### 2022-03-07 Manuscript/StandardizedEvaluation.Rmd
Version to compare with latex diff or pdf diff

<!-- The quality of a solution obtained by multiple imputation depends on the statistical properties of the incomplete data and the degree to which an imputation procedure is able to capture these properties when modeling missing values. In general it holds that modeling missing data becomes more challenging when the amount of missingness increases. However, when (strong) relations in the data are present, the observed parts can hold great predictive power for the models that estimate the missingness. In that case, multiple imputation would be substantially more efficient than the ubiquitous list-wise deletion. -->

@@

<!-- ~~However, because multiple imputation was designed as a mode for statistical inference, a minimal set of statistical properties should at least be evaluated. We highlight four aspects of evaluation that should be considered when evaluation imputation routines.~~ -->

>>>>

~~The quality of a solution obtained by multiple imputation depends on the statistical properties of the incomplete data and the degree to which an imputation procedure is able to capture these properties when modeling missing values. In general it holds that modeling missing data becomes more challenging when the amount of missingness increases. However, when (strong) relations in the data are present, the observed parts can hold great predictive power for the models that estimate the missingness. In that case, multiple imputation would be substantially more efficient than the ubiquitous list-wise deletion.~~

@@

~~However, because multiple imputation was designed as a mode for statistical inference, a minimal set of statistical properties should at least be evaluated. We highlight four aspects of evaluation that should be considered when evaluation imputation routines.~~
